Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-01-29 paper/compilation.tex
change failure safety wording.

Before checking if policies captured by the PGIR are safe, we minimize the PGIR to improve our safety analysis. 
The minimization is based on the observation that, although every path in the PGIR is a valid path in the topology, we do not want to consider paths that form loops. In particular, BGP's loop prevention mechanism forces an AS to reject any route for which it is already in the AS path.
%
For example, in Figure~\ref{fig:example-compilation}, the path $W \cdot A \cdot C \cdot B \cdot W$ is a valid topological path, leading to a path that satisfies the preference 1 policy, but which contains a loop.
%
It often simplifies the failure-safety analysis to eliminate cases that are not possible due to loops. 
%For example, if we can safely remove a PGIR edge, then we do not have to consider what happens when the edge has failed.
We use graph dominators~\cite{tarjan-dominance} as a cheap approximation for removing many nodes and edges in the PGIR that are never on any \emph{simple} (loop free) path between the start and end nodes.
In the PGIR, a node $x$ dominates a node $y$ if $x$ appears on every path leading to $y$ from the start node. Many efficient algorithms exist for finding graph dominators in practice~\cite{linear-dominance, fast-dominance, tarjan-dominance}.
%We can safely remove any PGIR node or edge as long as it never appears on any \emph{simple} path from the \textit{start} node to the \emph{end} node. 
For example, node $(W,1,1)$ in Figure~\ref{fig:example-compilation} is never on a simple path to the end node since it must go through another $W$ in either case.
Colored nodes and dashed edges are removed after minimization since they are irrelvant to the BGP decision process.
%
%Although fully minimizing this graph is an NP-complete problem,  a simple and efficient algorithm based on graph dominators achieves largely the same effect, greatly simplifying the failure safety analysis.

>>>>

Before checking if policies captured by the PGIR are safe, we minimize the PGIR to improve our safety analysis. 
The minimization is based on the observation that, although every path in the PGIR is a valid path in the topology, we do not want to consider paths that form loops. In particular, BGP's loop prevention mechanism forces an AS to reject any route for which it is already in the AS path.
%
For example, in Figure~\ref{fig:example-compilation}, the path $W \cdot A \cdot C \cdot B \cdot W$ is a valid topological path, leading to a path that satisfies the preference 1 policy, but which contains a loop.
%
It often improves the precision of the failure-safety analysis to eliminate cases that are not possible due to loops. 
%For example, if we can safely remove a PGIR edge, then we do not have to consider what happens when the edge has failed.
We use graph dominators~\cite{tarjan-dominance} as a cheap approximation for removing many nodes and edges in the PGIR that are never on any \emph{simple} (loop free) path between the start and end nodes.
In the PGIR, a node $x$ dominates a node $y$ if $x$ appears on every path leading to $y$ from the start node.
%We can safely remove any PGIR node or edge as long as it never appears on any \emph{simple} path from the \textit{start} node to the \emph{end} node. 
For example, node $(W,1,1)$ in Figure~\ref{fig:example-compilation} is never on a simple path to the end node since it must go through another $W$ in either case.
Colored nodes and dashed edges are removed after minimization since they are irrelvant to the BGP decision process.
%
%Although fully minimizing this graph is an NP-complete problem,  a simple and efficient algorithm based on graph dominators achieves largely the same effect, greatly simplifying the failure safety analysis.
